`r if (knitr::is_html_output()) '# References {-}
'`

```{r child = "README.md"}


```


```{r child = "General-links.md"}


```

[1] **Scholarly Context Not Found: One in Five Articles Suffers from Reference Rot**, Klein et al, https://doi.org/10.1371/journal.pone.0115253

[2] **Software citation principles**, Smith et al, https://doi.org/10.7717/peerj-cs.86

[3] **Code publication and citation**, Croucher et al, https://doi.org/10.5281/zenodo.801586




# Resources {.tabset .tabpills}

Over the past few years there has been a hige development of reproducible research tools using R.

## RStudio tools and packages

Since the development of R and RStudio (and a magnitude of other IT changes happening at the same time) there are now tools for working with issues to do with [reproducibility](https://www.nature.com/news/1-500-scientists-lift-the-lid-on-reproducibility-1.19970). There are many blogs from a simple web search. 

Here is a collection of the posts I have drawn inspiration from:

- [R bloggers post](https://www.r-bloggers.com/reproducible-research-and-r-workflow/): Jeromy Anglim
- [Reproducible workflows in RStudio](https://cyberhelp.sesync.org/basic-git-lesson/2016/08/25/)
- [R workflow](https://maraaverick.rbind.io/2017/09/r-workflow-fun/): Mara Averick
- [Methods in Ecology](https://methodsblog.com/2016/10/05/reproducibility-with-r/)
- [workflow general tips](https://csgillespie.github.io/efficientR/workflow.html)
- [Data Science and R/Python](https://community.rstudio.com/t/data-science-project-template-for-r/3230)
- [Truely reproducible](https://timogrossenbacher.ch/2017/07/a-truly-reproducible-r-workflow/)
- [EEB313H1](https://uoftcoders.github.io/rcourse/lec16-rmarkdown.html)

## Scientific publications

There are many many different posts on reproducible workflows. This document collects the current resources available in R and RMarkdown. I have developed this document from a combination of different git repositories:

- BES guidelines as a start
- Added Wickhams etc paper

* Best practices for Scientific Computing (http://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.1001745)

* Good enough practices for Scientific Computing (https://swcarpentry.github.io/good-enough-practices-in-scientific-computing/)

* 10 simple rules for reproducible computational research: http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1003285
* A quick guide to organizing computational biology projects: http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1000424
* Ten Simple Rules for Digital Data Storage (http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005097)
* The Reproducible Research CRAN Task View: (https://cran.r-project.org/web/views/ReproducibleResearch.html)

## Workflow options

However because of this my workflow has a distinctly ecological feel along with the tidyverse approach of [tooling](https://style.tidyverse.org/index.html). I apologise for this in advance. If you are not a R user I would recommend finding another workflow with the same components.

- [Packaging data publication](https://peerj.com/preprints/3192/)

- [Tidytools package]()

# Files within this repository {.tabset .tabpills}

Resources include the templates and resources within this repository.

```{r}
list.files("sections/")
```

## Checklist 

```{r child = here::here("sections/checklist/index.md")}

```

<!-- #  -->
<!-- #  -->
<!-- # date: "April 2019" -->
<!-- # output: -->
<!-- #   html_document: -->
<!-- #     theme: journal -->
<!-- #   pdf_document: default -->
<!-- #   word_document: -->
<!-- #     fig_caption: yes -->
<!-- # editor_options: -->
<!-- #   chunk_output_type: console -->
<!-- # bibliography: reproduce.bib -->

<!-- Developed from `misc{repro-guide, -->
<!-- title={{Reproducibility in Science: A Guide to enhancing reproducibility in scientific results and writing}}, -->
<!-- howpublished="url{http://ropensci.github.io/reproducibility-guide/}" -->
<!-- }` -->

This takes a combination of reproducible guides, inputs them into a bookdown project and begins to write R scripts to access the dynamic database of reproducibility literature underneath it.

## Coding groups

- [Uni of Toronto Coders](https://github.com/UofTCoders)
  -[R course](https://github.com/UofTCoders/rcourse)

# Software options

rOpenSci [is a non-profit initiative founded in 2011 by Karthik Ram, Scott Chamberlain, and Carl Boettiger to make scientific data retrieval reproducible. Over the past seven years we have developed an ecosystem of open source tools, we run annual unconferences, and review community developed software.](https://ropensci.org/about/)

They have produced a great interface for reproducible packages in R with documentation. The key software and packages I use for my workflow are:

## File building

Im not sure what this is actually meant to represent but I see these options as packages making [packages](https://wlandau.github.io/2016/06/14/workflow/)

### packrat

In mid-August of 2016, Eric Nantz of the R-Podcast converted me to packrat (by Kevin Ushey and others at RStudio), a package that lengthens the shelf life of R projects. [Packrat](https://rstudio.github.io/packrat/) maintains local snapshots of dependencies so that your project won't break when external packages are updated. Just be sure your current working directory is the root directory of your project when you run remake::make() or the Makefile. Also, if you use a shell.sh with your Makefile, be sure to modify module load R so that it points to the version of R corresponding to your packrat library. You can learn more about packrat with the hands-on walkthrough.

### ProjectTemplate

- [ProjectTemplate](https://cran.r-project.org/web/packages/ProjectTemplate/ProjectTemplate.pdf) and the webpage is [here](http://projecttemplate.net/).
- A workshop using this [package](https://github.com/jeromyanglim/leuven2016rworkshop)

## Packages

Hadley wickham book on [R Packages](http://r-pkgs.had.co.nz/).

### R

- [rrtools](https://github.com/benmarwick/rrtools)



## Version control



## Markdown


