--- 
title: "Reproducible guide"
subtitle: 'Draft 2022'
date: "`r Sys.Date()`"
author: "Anthony Davidson"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib, references.bib, reproduce.bib]
description: |
  Over the past few years there has been a hige development of reproducible research tools using R.
link-citations: yes
mathjax: "https://cdnjs.cloudflare.com/ajax/libs/mathjax/2.7.5/MathJax.js?config=TeX-AMS_CHTML.js"
---

```{r globaloptions, message=FALSE, warning=FALSE, include=FALSE}

library(here)
library(tidyverse)
library(ezknitr) 
library(knitr) 
library(devtools) 
# export .r code only
# knitr::purl("FILE")


#document global rules
knitr::opts_chunk$set(comment=NA,echo=FALSE,message=FALSE,warning=FALSE,fig.path="figures/",fig.width=6.5,fig.height=4,fig.align="center")
```

<!-- Generated from README information so as not to re-write -->

# Overview {#nice-label .tabset .tabpills}

This guide is a combination of resources for reproducible and open science tools for graduate research and beyond using RMarkdown and RStudio.

```{r child = "README.md"}

```

If you prefer text as the link instead of a numbered reference use: [any text you want can go here](#nice-label).

## Working with this resource {.tabset .tabpills}

```{r child = "sections/writingCode/index.md"}
```

```{r}
# [coming soon README child here]
# future code developement concepts
# libraries needed
# source("./Rcode/r-packages-needed.R", echo = FALSE)

# themes
# source("./Rcode/davidson-2019-theme.r", echo = FALSE)

#overall code
# source("./Rcode/manuscript-source-code.R", echo = FALSE)
```

## Packages and libraries needed:

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
